Dominance Regions for Affine Cluster Algebras

### 2022-07-01 affine_dominance.tex
Change of conventions (lots of clean-up still needed), but Proposition 5.7 should now be correct as stated

\newcommand{\Aut}{\operatorname{Aut}}
\newcommand{\Col}{\operatorname{Col}}
\newcommand{\diag}{\operatorname{diag}}
\newcommand{\dpt}{\operatorname{dp}}
\newcommand{\hgt}{\operatorname{ht}}
\newcommand{\Id}{\operatorname{Id}}
\newcommand{\into}{\hookrightarrow}
\newcommand{\obeta}{{\overline{\beta}}}
\newcommand{\oi}{{\overline{\imath}}}
\newcommand{\ot}{{\overline{t}}}
\newcommand{\rsh}{{\operatorname{rsh}}}
\newcommand{\sh}{{\operatorname{sh}}}
\newcommand{\WA}{{W\!\!A}}
\newcommand{\wt}{{\operatorname{wt}}}

@@

  Let $B=(b_{ij})$ denote an acyclic $n\times n$ exchange matrix.
  Write $Q_B$ for the corresponding quiver, here $b_{ij}>0$ means there is an arrow from $j$ to $i$ in $Q$.
  \sayDR{Note that $Q_B$ is only recording the orientations of edges.}
  Without loss of generality we assume $1,\ldots,n$ is a sink adapted sequence for $Q_B$, i.e. vertex $1$ is a sink and vertex $n$ is a source in $Q$.
  This implies $B$ has positive entries above the diagonal.
  \sayDR{This seemed to give the cleanest calculation.}
  Define vectors $\bfc^{(r)}_k\in\ZZ^n$ for $1\le k\le n$ and $r\in\ZZ$ recursively as follows:
  \begin{itemize}
    \item for $-n\le r\le 0$, we have $\bfc^{(r)}_k=\bfe_k$ for $1\le k\le r+n$ and $\bfc^{(r)}_k=-\bfe_k$ for $r+n<k\le n$, where $\bfe_k
      $ is the standard basis vector;
    \item for $r=ns+\ell>0$ with $1 \le \ell \le n$, we have $\bfc^{(r)}_k=\begin{cases} -\bfc^{(r-1)}_k & \text{if $\ell=k$;}\\ \bfc^{(r-1)}_k+b_{\ell k}\bfc^{(r-1)}_\ell & \text{if $\ell<k$;}\\ \bfc^{(r-1)}_k-b_{\ell k}\bfc^{(r-1)}_\ell & \text{if $\ell>k$.} \end{cases}$
    \item for $r=ns+\ell<-n$ with $1 \le \ell \le n$, we have $\bfc^{(r-1)}_k=\begin{cases} -\bfc^{(r)}_k & \text{if $\ell=k$;}\\ \bfc^{(r)}_k-b_{\ell k}\bfc^{(r)}_\ell & \text{if $\ell<k$;}\\ \bfc^{(r)}_k+b_{\ell k}\bfc^{(r)}_\ell & \text{if $\ell>k$.} \end{cases}$
  \end{itemize}
  For $r\in\ZZ$ and $1\le k\le n$, write $r\equiv_n k$ if $n|(r-k)$ and $r\not\equiv_n k$ otherwise.
  \begin{lemma}
    \label{lem:tropical signs}
    Assume $B$ is not finite-type.
    \begin{itemize}
      \item For $r\in\ZZ_{>0}$, the vector $\bfc^{(r)}_k$ is non-negative if $r\not\equiv_n k$ and non-positive when $r\equiv_n k$.
      \item For $r\in\ZZ_{<-n}$, the vector $\bfc^{(r)}_k$ is non-negative if $r\equiv_n k$ and non-positive when $r\not\equiv_n k$.
    \end{itemize}
  \end{lemma}
  \begin{proof}
    Induction
  \end{proof}

@@

  Let $\TT_n$ denote the $n$-regular labeled tree with root vertex $t_0$.
  Define vertices $t_r\in\TT_n$ for $r\in\ZZ$ by joining $t_{r-1}$ to $t_r$ by an edge labeled $\ell$ if $r\equiv_n\ell$.
  Since $1,\ldots,n$ is sink adapted, this labels preprojective seeds by positive integers and postinjective seeds by negative integers.
  Write $\tilde B^{t_r}$ for the extended exchange matrix associated to the seed at $t_r$.
  \begin{lemma}
    \label{lem:preprojective exchange matrices}
    For $r\in\ZZ$ with $r=ns+\ell$ for $1\le \ell \le n$, the matrix $\tilde B^{t_r}$ has principal part given by $b^{t_r}_{ij}=(-1)^{\epsilon(i,\ell)+\epsilon(j,\ell)}b_{ij}$ for $\epsilon(i,j)=\begin{cases} 1 & \text{if $i\le j$;}\\ 0 & \text{otherwise;}\end{cases}$ and the $\bfc$-vector part of the $k$-th column is given by $\bfc^{(r)}_k$ for $1\le k\le n$.
  \end{lemma}
  \begin{proof}
    We work by upward and downward induction on $r$.
    \sayDR{Downward case still needed}
    For $r=0$, we just get $\tilde B$ and the claim clearly holds.
    Assume the claim holds for $r-1$, we show the claim holds for $r$.

@@

@@

  It follows that we may write explicit expressions for the $2n\times 2n$ mutation matrices $E^{t_r}_{k,\varepsilon}$ for $r\ge0$.
  Indeed, taking $r=ns+\ell$ with $1 \le \ell \le n$ we get $E^{t_r}_{k,\varepsilon}=(e^{t_r}_{ij})$ with
  \begin{equation}
    \label{eq:preprojective mutation matrices}
    e^{t_r}_{ij}=\begin{cases} 1 & \text{if $i=j\ne k$;}\\ -1 & \text{if $i=j=k$;}\\ b_{ik} & \text{if $\varepsilon=+$ and $i<j=k\le\ell$ or $j=k\le\ell<i$ or $\ell<i<j=k$;}\\ -b_{ik} & \text{if $\varepsilon=-$ and $j=k<i\le\ell$ or $i\le\ell<j=k$ or $\ell<j=k<i$;} \\ 0 & \text{otherwise;} \end{cases}
  \end{equation}
  where the bottom $n$ entries in column $k$ are given as follows:
  \begin{itemize}
    \item if $\varepsilon=+$, we have $\bfc^{(r)}_k$ if $r\not\equiv_n k$ and zero otherwise;
    \item if $\varepsilon=-$, we have $-\bfc^{(r)}_k$ if $r\equiv_n k$ and zero otherwise.
  \end{itemize}

  \[
    \left[\begin{array}{cc|c|cccc}
      0 & + & + & - & - & \cdots & -\\
      - & 0 & + & - & - & \cdots & -\\
      \hline
      - & - & 0 & - & - & \cdots & -\\
      \hline
      + & + & + & 0 & + & \cdots & +\\
      + & + & + & - & 0 & \cdots & +\\
      \vdots & \vdots & \vdots & \vdots & \vdots & \ddots & \vdots\\
      + & + & + & - & - & \cdots & 0
    \end{array}\right]
    \qquad
    \left[\begin{array}{cccc|c|cc}
      0 & \cdots & + & + & - & - & -\\
      \vdots & \ddots & \vdots & \vdots & \vdots & \vdots & \vdots\\
      - & \cdots & 0 & + & - & - & -\\
      - & \cdots & - & 0 & - & - & -\\
      \hline
      + & \cdots & + & + & 0 & + & +\\
      \hline
      + & \cdots & + & + & - & 0 & +\\
      +& \cdots & + & + & - & - & 0
    \end{array}\right]
  \]

  For $\lambda\in\ZZ^n$ and $r\in\ZZ_{>0}$ with $r=ns+\ell$ for $1\le\ell\le n$, the tropical transformation $\phi_{t_r}(\lambda)$ is given by
  \[
    E^{t_{r-1}}_{\ell,\varepsilon_r} \cdots E^{t_{r-\ell}}_{1,\varepsilon_{r-\ell+1}} E^{t_{ns-1}}_{n,\varepsilon_{ns}} \cdots E^{t_1}_{2,\varepsilon_2} E^{t_0}_{1,\varepsilon_1} \lambda
  \]
  for a sequence of signs $\varepsilon_1,\ldots,\varepsilon_r$ depending on $\lambda$.
  Similarly, the tropical transformation $\phi_{t_{-r}}(\lambda)$ is given by
  \[
    E^{t_{-r+1}}_{n-\ell+1,\varepsilon_{-r}} \cdots E^{t_{-r+\ell}}_{n,\varepsilon_{-r+\ell-1}} E^{t_{-ns+1}}_{1,\varepsilon_{-ns}} \cdots E^{t_{-1}}_{n-1,\varepsilon_{-2}} E^{t_0}_{n,\varepsilon_{-1}} \lambda
  \]
  for a sequence of signs $\varepsilon_{-1},\ldots,\varepsilon_{-r}$ depending on $\lambda$.
  \begin{lemma}
    \label{lem:imaginary mutations}
    If $\lambda\in\ZZ^n$ is imaginary, then every sign $\varepsilon_r$ with $r>0$ above is equal to $-$ and every sign $\varepsilon_r$ with $r<0$ above is equal to $+$.
  \end{lemma}
  \begin{proof}
    With $1,\ldots,n$ being sink adapted, these sign choices give the most complicated transformation at each step.
    That should mean that $\lambda$ is sufficiently far from the initial chamber and remains there under all mutations.
  \end{proof}

@@

  Define an infinite quiver $\widehat{Q}$ with vertices $(k,s)\in [n]\times\ZZ_{\ge0}$ and the following arrows:
  \begin{itemize}
    \item an arrow $(\ell,s)\to (k,s)$ of weight $b_{k\ell}$ whenever $k<\ell$ and $s\ge0$;
    \item an arrow $(k,s+1)\to (\ell,s)$ of weight $-b_{k\ell}$ whenever $k<\ell$ and $s\ge0$;
    \item an arrow $(k,s+1)\to (k,s)$ of weight $-1$ whenever $s\ge0$.
  \end{itemize}
  Given a path $p$ in $\widehat{Q}$, write $\wt(p)$ for the product of the weights along the arrows in $p$.
  Let $i(p)$ and $t(p)$ denote the initial and terminal vertex along the path $p$.
  Write $\hgt(p)$ for the largest $s$ appearing as the second component of a vertex along the path $p$.
  Then for $r<0$ with $r=ns+\ell$ for $1\le\ell\le n$, we have
  \[\lambda'_k=\begin{cases}\sum\limits_{\substack{p\subset\widehat{Q}\\ \hgt(p)=-s-1, t(p)=(k,0)}}\wt(p)\lambda_{i(p)} & \text{if $1\le k\le\ell-1$;}\\ \sum\limits_{\substack{p\subset\widehat{Q}\\ \hgt(p)=-s, t(p)=(k,0)}}\wt(p)\lambda_{i(p)} & \text{if $\ell\le k\le n$;} \end{cases}\]

>>>>

\newcommand{\Aut}{\operatorname{Aut}}
\newcommand{\beps}{{\boldsymbol{\varepsilon}}}
\newcommand{\Col}{\operatorname{Col}}
\newcommand{\diag}{\operatorname{diag}}
\newcommand{\dpt}{\operatorname{dp}}
\newcommand{\hgt}{\operatorname{ht}}
\newcommand{\Id}{\operatorname{Id}}
\newcommand{\into}{\hookrightarrow}
\newcommand{\obeta}{{\overline{\beta}}}
\newcommand{\oi}{{\overline{\imath}}}
\newcommand{\ot}{{\overline{t}}}
\newcommand{\rsh}{{\operatorname{rsh}}}
\newcommand{\sh}{{\operatorname{sh}}}
\newcommand{\WA}{{W\!\!A}}
\newcommand{\wt}{{\operatorname{wt}}}

@@

  Let $B=(b_{ij})$ denote an acyclic $n\times n$ exchange matrix.
  Write $Q_B$ for the corresponding quiver, here $b_{ij}>0$ means there is an arrow from $j$ to $i$ in $Q$.
  \sayDR{Note that $Q_B$ is only recording the orientations of edges.}
  Without loss of generality, we assume $1,\ldots,n$ is a source adapted sequence for $Q_B$, i.e. vertex $1$ is a source and vertex $n$ is a sink in $Q$.
  This implies $B$ has positive entries below the diagonal.
  \sayDR{I changed back because of a stupid discrepancy between signs.}
  Define vectors $\bfc^{(r)}_k\in\ZZ^n$ for $1\le k\le n$ and $r\in\ZZ$ recursively as follows:
  \begin{itemize}
    \item for $0\le r\le n$, we have $\bfc^{(r)}_k=-\bfe_k$ for $1\le k\le r$ and $\bfc^{(r)}_k=\bfe_k$ for $r<k\le n$, where $\bfe_k$ is the standard basis vector;
    \item for $r=ns+\ell>n$ with $1 \le \ell \le n$, we have $\bfc^{(r)}_k=\begin{cases} -\bfc^{(r-1)}_k & \text{if $k=\ell$;}\\ \bfc^{(r-1)}_k-b_{\ell k}\bfc^{(r-1)}_\ell & \text{if $k>\ell$;}\\ \bfc^{(r-1)}_k+b_{\ell k}\bfc^{(r-1)}_\ell & \text{if $k<\ell$.} \end{cases}$
    \item for $r=ns+\ell\le 0$ with $1 \le \ell \le n$, we have $\bfc^{(r-1)}_k=\begin{cases} -\bfc^{(r)}_k & \text{if $k=\ell$;}\\ \bfc^{(r)}_k-b_{\ell k}\bfc^{(r)}_\ell & \text{if $k>\ell$;}\\ \bfc^{(r)}_k+b_{\ell k}\bfc^{(r)}_\ell & \text{if $k<\ell$.} \end{cases}$
  \end{itemize}

  For $r\in\ZZ$ and $1\le k\le n$, write $r\equiv_n k$ if $n|(r-k)$ and $r\not\equiv_n k$ otherwise.
  \begin{lemma}
    \label{lem:tropical signs}
    Assume $B$ is not finite-type.
    \begin{itemize}
      \item For $r\in\ZZ_{>n}$, the vector $\bfc^{(r)}_k$ is non-negative if $r\equiv_n k$ and non-positive when $r\not\equiv_n k$.
      \item For $r\in\ZZ_{<0}$, the vector $\bfc^{(r)}_k$ is non-negative if $r\not\equiv_n k$ and non-positive when $r\equiv_n k$.
    \end{itemize}
  \end{lemma}
  \begin{proof}
    Induction
  \end{proof}

@@

  Let $\TT_n$ denote the $n$-regular labeled tree with root vertex $t_0$.
  Define vertices $t_r\in\TT_n$ for $r\in\ZZ$ by joining $t_{r-1}$ to $t_r$ by an edge labeled $\ell$ if $r\equiv_n\ell$.
  Since $1,\ldots,n$ is source adapted, this labels preprojective seeds by negative integers and postinjective seeds by positive integers.
  Write $\tilde B^{t_r}$ for the extended exchange matrix associated to the seed at $t_r$.
  \begin{lemma}
    \label{lem:transjective exchange matrices}
    For $r\in\ZZ$ with $r=ns+\ell$ for $1\le \ell \le n$, the matrix $\tilde B^{t_r}$ has principal part given by $b^{t_r}_{ij}=(-1)^{\epsilon(i,\ell)+\epsilon(j,\ell)}b_{ij}$ for $\epsilon(i,j)=\begin{cases} 1 & \text{if $i\le j$;}\\ 0 & \text{otherwise;}\end{cases}$ and the $\bfc$-vector part of the $k$-th column is given by $\bfc^{(r)}_k$ for $1\le k\le n$.
  \end{lemma}
  \begin{proof}
    We work by upward and downward induction on $r$.
    \sayDR{Downward case still needed}
    For $r=0$, we just get $\tilde B$ and the claim clearly holds.
    Assume the claim holds for $r-1$, we show the claim holds for $r$.

@@

    ***The next part needs adjustment since the source-sink convention changed***

@@

  It follows that we may write explicit expressions for the $2n\times 2n$ mutation matrices $E^{t_r}_{k,\varepsilon}$.
  Indeed, taking $r=ns+\ell>n$ with $1 \le \ell \le n$ we get $E^{t_r}_{k,\varepsilon}=(e^{t_r}_{ij})$ with
  \begin{equation}
    \label{eq:postinjective mutation matrices}
    e^{t_r}_{ij}=
    \begin{cases}
      1 & \text{if $i=j\ne k$;}\\
      -1 & \text{if $i=j=k$;}\\
      b_{ik} & \text{if $\varepsilon=-$ and $j=k\le\ell<i$;}\\
      -b_{ik} & \text{if $\varepsilon=-$ and $i<j=k\le\ell$ or $\ell<i<j=k$;}\\
      b_{ik} & \text{if $\varepsilon=+$ and $j=k<i\le\ell$ or $\ell<j=k<i$;}\\
      -b_{ik} & \text{if $\varepsilon=+$ and $i\le\ell<j=k$;}\\
      0 & \text{otherwise;}
    \end{cases}
  \end{equation}
  where the bottom $n$ entries in column $k$ are given as follows:
  \begin{itemize}
    \item if $\varepsilon=+$, we have $\bfc^{(r)}_k$ if $r\equiv_n k$ and zero otherwise;
    \item if $\varepsilon=-$, we have $-\bfc^{(r)}_k$ if $r\not\equiv_n k$ and zero otherwise.
  \end{itemize}

  \begin{remark}
  The result after mutation:
  \[
    \left[\begin{array}{cc|c|cccc}
      0 & - & - & + & + & \cdots & +\\
      + & 0 & - & + & + & \cdots & +\\
      \hline
      + & + & 0 & + & + & \cdots & +\\
      \hline
      - & - & - & 0 & - & \cdots & -\\
      - & - & - & + & 0 & \cdots & -\\
      \vdots & \vdots & \vdots & \vdots & \vdots & \ddots & \vdots\\
      - & - & - & + & + & \cdots & 0
    \end{array}\right]
    \qquad
    \left[\begin{array}{cccc|c|cc}
      0 & \cdots & - & - & + & + & +\\
      \vdots & \ddots & \vdots & \vdots & \vdots & \vdots & \vdots\\
      + & \cdots & 0 & - & + & + & +\\
      + & \cdots & + & 0 & + & + & +\\
      \hline
      - & \cdots & - & - & 0 & - & -\\
      \hline
      - & \cdots & - & - & + & 0 & -\\
      - & \cdots & - & - & + & + & 0
    \end{array}\right]
  \]
  \end{remark}

  For $\lambda\in\ZZ^n$ and $r\in\ZZ_{>0}$ with $r=ns+\ell$ for $1\le\ell\le n$, the tropical transformation $\phi_{t_r}(\lambda)$ is given by
  \[
    E^{t_{r-1}}_{\ell,\varepsilon_r} \cdots E^{t_{r-\ell}}_{1,\varepsilon_{r-\ell+1}} E^{t_{ns-1}}_{n,\varepsilon_{ns}} \cdots E^{t_1}_{2,\varepsilon_2} E^{t_0}_{1,\varepsilon_1} \lambda
  \]
  for a sequence of signs $\varepsilon_1,\ldots,\varepsilon_r$ depending on $\lambda$.
  Similarly, the tropical transformation $\phi_{t_{-r}}(\lambda)$ is given by
  \[
    E^{t_{-r+1}}_{n-\ell+1,\varepsilon_{-r}} \cdots E^{t_{-r+\ell}}_{n,\varepsilon_{-r+\ell-1}} E^{t_{-ns+1}}_{1,\varepsilon_{-ns}} \cdots E^{t_{-1}}_{n-1,\varepsilon_{-2}} E^{t_0}_{n,\varepsilon_{-1}} \lambda
  \]
  for a sequence of signs $\varepsilon_{-1},\ldots,\varepsilon_{-r}$ depending on $\lambda$.
  \begin{lemma}
    \label{lem:imaginary mutations}
    If $\lambda\in\ZZ^n$ is imaginary, then every sign $\varepsilon_r$ with $r>0$ above is equal to $+$ and every sign $\varepsilon_r$ with $r<0$ above is equal to $-$.
  \end{lemma}
  \begin{proof}
    With $1,\ldots,n$ being source adapted, these sign choices give the most complicated transformation at each step.
    That should mean that $\lambda$ is sufficiently far from the initial chamber and remains there under all mutations.
  \end{proof}

@@

  Given a sequence of signs $\beps=(\varepsilon_1,\varepsilon_2,\ldots,\varepsilon_r)$ with $\varepsilon_i\in\{\pm\}$, define a quiver $Q^{(r)}_\beps$ with vertices $(\ell,s)\in [n]\times\ZZ_{\ge0}$ satisfying $ns+\ell\le n+r$ and having the following arrows:
  \begin{itemize}
    \item an arrow $(\ell,s)\to (k,s)$ of weight $b_{k\ell}$ whenever $\ell<k$, $ns+\ell\le r$, and $\varepsilon_{ns+\ell}=+$;
    \item an arrow $(\ell,s)\to (k,s+1)$ of weight $-b_{k\ell}$ whenever $k<\ell$, $ns+\ell\le r$, and $\varepsilon_{ns+\ell}=+$;
    \item an arrow $(\ell,s)\to (\ell,s+1)$ of weight $-1$ whenever $ns+\ell\le r$.
  \end{itemize}
  For $1\le\ell\le r$, write $\hat{\ell}$ for the vertex $(\ell,s)$ of $Q^{(r)}_\beps$ with $s$ maximal.
  Below we freely identify each vertex $(\ell,0)$ with $\ell$.

  Given a path $\fp\subset Q^{(r)}_\beps$, write $\wt(\fp)$ for the product of the weights along the arrows in $\fp$.
  Let $i(\fp)$ and $t(\fp)$ denote the initial and terminal vertex along the path $\fp$.
  Below we only consider paths $\fp\subset Q^{(r)}_\beps$ with $i(\fp)=(\ell,0)$ for some $\ell$.
  \begin{proposition}
    Consider $r>0$ with $r=ns+\ell$ for $1\le\ell\le n$.
    For $\lambda\in\ZZ^n$, suppose the tropical transformation $\phi_{t_r}(\tilde\lambda)=(\lambda'_1,\ldots,\lambda'_n,\lambda'_{n+1},\cdots,\lambda'_{2n})$ is given by
    \[
      E^{t_{r-1}}_{\ell,\varepsilon_r} \cdots E^{t_{r-\ell}}_{1,\varepsilon_{r-\ell+1}} E^{t_{ns-1}}_{n,\varepsilon_{ns}} \cdots E^{t_1}_{2,\varepsilon_2} E^{t_0}_{1,\varepsilon_1} \lambda
    \]
    with the signs $\beps=(\varepsilon_1,\cdots,\varepsilon_r)$ determined by $\lambda$.
    Then
    \[
      \lambda'_k=\sum\limits_{\fp\subset Q^{(r)}_\beps, t(\fp)=\hat{k}} \wt(\fp)\lambda_{i(\fp)}.
    \]
    and $\lambda'_{n+k}=0$ for $1\le k\le n$ and $r<0$ if $\varepsilon_i=-$ for all $i$.
    \sayDR{We need this for arbitrary sequences of signs and to include $r>0$.}
  \end{proposition}
  \begin{proof}
    We work by induction on $r$.
    Write $r=ns+\ell$.
    From Lemma~\ref{lem:transjective exchange matrices} and Lemma~\ref{lem:tropical signs}, we see that the $\ell$-th column of $\tilde B^{t_{r-1}}$ has the first $n$ entries non-negative and the last $n$ entries non-positive.

    Writing $\phi_{t_{r-1}}(\tilde\lambda)=(\lambda''_1,\ldots,\lambda''_{2n})$ we also see from Lemma~\ref{lem:transjective exchange matrices} that $\phi_{t_r}(\tilde\lambda)=E^{t_{r-1}}_{\ell,\varepsilon_r}\phi_{t_{r-1}}(\tilde\lambda)$ is given by
    \[
      \begin{cases}
        (\lambda''_1-b_{1\ell}\lambda''_\ell,\ldots,\lambda''_{\ell-1}-b_{\ell-1,\ell}\lambda''_\ell,-\lambda''_\ell,\lambda''_{\ell+1}+b_{\ell+1,\ell}\lambda''_\ell,\ldots,\lambda''_n+b_{n\ell}\lambda''_\ell,\lambda''_{n+1},\ldots,\lambda''_{2n}) & \text{if $\varepsilon_r=+$;}\\
        (\lambda''_1,\ldots,\lambda''_{\ell-1},-\lambda''_\ell,\lambda''_{\ell+1},\ldots,\lambda''_n,\lambda''_{n+1}-b^{t_{r-1}}_{n+1,\ell}\lambda''_\ell,\ldots,\lambda''_{2n}-b^{t_{r-1}}_{2n,\ell}\lambda''_\ell) & \text{if $\varepsilon_r=-$.}\\
      \end{cases}
    \]
    Iterating this, starting from $\ell=1$, we obtain the formula
    \begin{equation}
      \lambda'_k=
      \begin{cases} 
        -\lambda_k-\sum\limits_{1\le \ell_1<\cdots<\ell_m\le \ell} (-1)^m b_{k\ell_m} \prod\limits_{w=2}^m b_{\ell_w \ell_{w-1}}\lambda_{\ell_1} & \text{if $1\le k\le \ell$.}\\
        \lambda_k+\sum\limits_{1\le \ell_1<\cdots<\ell_m\le \ell} (-1)^m b_{k\ell_m} \prod\limits_{w=2}^m b_{\ell_w \ell_{w-1}}\lambda_{\ell_1} & \text{if $\ell+1\le k\le n$;}
      \end{cases}
    \end{equation}
    for $1\le k\le n$ when $s=0$.
  \end{proof}

  Then for $r<0$ with $r=ns+\ell$ for $1\le\ell\le n$, we have
  \[\lambda'_k=\begin{cases}\sum\limits_{\substack{p\subset\widehat{Q}_\beps\\ \hgt(p)=-s-1, t(p)=(k,0)}}\wt(p)\lambda_{i(p)} & \text{if $1\le k\le\ell-1$;}\\ \sum\limits_{\substack{p\subset\widehat{Q}\\ \hgt(p)=-s, t(p)=(k,0)}}\wt(p)\lambda_{i(p)} & \text{if $\ell\le k\le n$;} \end{cases}\]
